Title

### 2018-11-20 MAESTROeX_I/paper.tex
possible sign error

First, we compute the time-centered edge velocities, $\Ub^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ub^n$ to $\Ub^{n+1,\dagger}$ by discretizing 
equation (\ref{eq:u_update}) as
\begin{eqnarray}
\Ub^{n+1,\dagger} 
&=& \Ub^n - \dt \left[\uadvtwo \cdot \nabla \Ub^{\nph,\pred} \right] \nonumber \\
&& - \dt \left[ - \frac{1}{\rho^\nph} \mathbf{G} \pi^\nmh + \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],\nonumber \\
\end{eqnarray}
where $\mathbf{G}$ approximates a cell-centered gradient from nodal
data.  Again, the $\dagger$ superscript refers 
to the fact that the updated velocity does not satisfy the divergence 
constraint.

>>>>

First, we compute the time-centered edge velocities, $\Ub^{\nph,\pred}$.
Then, we define
\begin{equation}
\rho^\nph = \frac{\rho^n + \rho^{n+1}}{2}, \qquad \rho_0^\nph = \frac{\rho_0^n + \rho_0^{n+1}}{2}.
\end{equation}
We update the velocity field $\Ub^n$ to $\Ub^{n+1,\dagger}$ by discretizing
equation (\ref{eq:u_update}) as
\begin{eqnarray}
\Ub^{n+1,\dagger}
&=& \Ub^n - \dt \left[\uadvtwo \cdot \nabla \Ub^{\nph,\pred} \right] \nonumber \\
&& - \dt \left[ - \frac{1}{\rho^\nph} \mathbf{G} \pi^\nmh + \frac{\left(\rho^\nph-\rho_0^\nph\right)}{\rho^\nph} g^{\nph} \eb_r \right],\nonumber \\
\end{eqnarray}
\MarginPar{I don't think there should be a minus sign in front of the $-\frac{1}{\rho}\mathbf{G} \pi$ term as this has been moved outside the brackets.}
where $\mathbf{G}$ approximates a cell-centered gradient from nodal
data.  Again, the $\dagger$ superscript refers
to the fact that the updated velocity does not satisfy the divergence
constraint.
